GMSE: an R package for generalised management strategy evaluation

### 2017-11-08 notebook/ms/SI1.Rmd
Few key equations

Key data structures used
================================================================================

@@

Manager fitness is affected by a manager's utility for resources and the projected change in resource abundance caused by the manager's policy. Manager utility is defined as the difference between `manage_target` and the estimation of population abundance as produced by the GMSE observation model. Manager utility can therefore change in each GMSE time step as resource abundance (and its estimate) changes; when the estimated resource abundance is greater than `manage_target`, manager utility is negative, and when the estimated resource abundance is less than `manage_target`, manager utility is positive.

>>>>

<a name="Key_data_structures_used">Key data structures used
================================================================================

@@

Manager fitness is affected by a manager's utility for resources and the projected change in resource abundance caused by the manager's policy. Manager utility is defined as the difference between `manage_target` and the estimation of population abundance as produced by the GMSE observation model (see "[Key data structures used](#Key_data_structures_used)" above). Manager utility can therefore change in each GMSE time step as resource abundance (and its estimate) changes; when the estimated resource abundance is greater than `manage_target`, manager utility is negative, and when the estimated resource abundance is less than `manage_target`, manager utility is positive. To get fitness, first the change in resource abundance ($\Delta A$) predicted by the manager's policy is calculated, and the squared difference between $\Delta A$ and the manager utility ($U_{manager}$) is calculated to obtain a utility deviation for the individual $i$,

$$ D_{i} = (\Delta A - U_{manager})^2.$$

The value of $D_{i}$ increases as $\Delta A$ gets further from $U_{manager}$; i.e, $D_{i}$ is high when manager's set policy that does not get closer to their `manage_target` abundance. Fitness is defined by first finding the maximum $D_{i}$ value among all `ga_popsize` individuals ($D_{max}$), then subracting this value from $D_{i}$ for each individual,

$$ Fitness_{i} = D_{max} - D_{i}.$$
